Lightweight Scheduling for the PRAGMA Cloud Testbed

### 2016-07-17 paper.tex
Few more tweaks to new sentences

\begin{enumerate}
\item A user does a general search for available resources based on the number of CPUs, memory size, and networking configuration (e.g., IPOP, ViNE~\cite{vine}, or PRAGMA-ENT) that is needed.  
\item Available resources that fit the criteria are displayed to the user and their availability is shown in a calendar layout.  
\item The user selects the desired resources, the timeframe, virtual cluster image, and configuration details and submits them to the Cloud scheduler.
Once the reservation is verified and confirmed, the user will get an email confirmation.  In the event two users try to reserve the same resource 
the same time, for example, one user has taken the resources while the second user was filling in the reservation fields, the second user will get 
a failure notification after hitting the submit button, and later via email.
\item When the reservation is ready to be activated, the cloud scheduler will use PCC and pragma\_boot to launch the virtual cluster, automatically configure the private and public network configuration on the virtual cluster nodes, and email the user when the reconfigured cluster is ready.   
\end{enumerate}

@@

We still need to address the race condition scenario where two users might try to reserve the same resources at the same time.  Booked currently 
does not have any mechanisms in place that can handle two simultaneous user requests for the same resources gracefully. 
The solution will need to be added in the future.  We also do not handle hardware failures at resource sites. When a virtual 
cluster goes down the failure will be recorded but we cannot accommodate a cluster relocation.  For fault tolerance of the cloud scheduler, we will
deploy a backup instance at a differnt site so that we can do a cloud scheduler server failover.

@@

In the pilot implementation of the cloud scheduler  we made a lot of simplifying assumptions, and  our future work will address them.  
Currently, the virtual cluster startup latency from the reservation to its availability to the user has not been analyzed in detail; but we observed
it is on the order of tens of minutes.   Multiple factors influence this latency, such as the underlying virtualization manager and load on the
physical system where the virtual cluster is instantiated. There is additional latency if the cluster image is not available on the site as it will
need to be downloaded from a remote repository and processed to make it available on the site. While this applies only to the first virtual cluster instantiation, it can add a considerable time  latency  depending on the cluster image size and the network speed from the site to the remote repository.

In the future when we use deployment on more sites, we can gather statistics on the cloud scheduler's usability and user experiences with virtual
clusters startup latencies in addition to its applicability to different scenarios.   We will also work on integrating IPOP and PRAGMA-ENT into the
cloud scheduler.  Next, we will rework the PCC software and integrate HTCondor so it is used in personal mode allowing us to keep a light footprint on
each of the PRAGMA sites.  Finally, we will investigate using the CloudFront option in pragma\_boot to manage application-specific  virtual cluster
images and staging them to the sites.     We will package and document the resulting software so that new users can quickly start using the PRAGMA cloud testbed as an experimental service to test new science and infrastructure tools.

>>>>

\begin{enumerate}
\item A user does a general search for available resources based on the number of CPUs, memory size, and networking configuration (e.g., IPOP, ViNE~\cite{vine}, or PRAGMA-ENT) that is needed.  
\item Available resources that fit the criteria are displayed to the user and their availability is shown in a calendar layout.  
\item The user selects the desired resources, the timeframe, virtual cluster image, and configuration details and submits them to the Cloud scheduler.
Once the reservation is verified and confirmed, the user will get an email confirmation.  In the event two users try to reserve the same resource 
at the same time, for example, one user has taken the resources while the second user was filling in the reservation fields, the second user will get 
a failure notification after hitting the submit button.
\item When the reservation is ready to be activated, the cloud scheduler will use PCC and pragma\_boot to launch the virtual cluster, automatically configure the private and public network configuration on the virtual cluster nodes, and email the user when the reconfigured cluster is ready.   
\end{enumerate}

@@

We still need to address the race condition scenario where two users might try to reserve the same resources at the same time.  Booked currently 
does not have any mechanisms in place that can handle two simultaneous user requests for the same resources gracefully. 
We also do not handle hardware failures at resource sites. When a virtual 
cluster goes down, the failure will be recorded but it will not be relocated to a different site.  We do plan to address the fault tolerance of the cloud scheduler by
deploying a backup instance at a different site so that we can failover when needed.

@@

In the pilot implementation of the cloud scheduler  we made a lot of simplifying assumptions, and  our future work will address them.  
Currently, the virtual cluster startup latency from the reservation to its availability to the user has not been analyzed in detail but we observed
it is on the order of tens of minutes.   Multiple factors influence this latency, such as the underlying virtualization manager and load on the
physical system where the virtual cluster is instantiated. There is additional latency if the cluster image is not available on the site as it will
need to be downloaded from a remote repository and processed to make it available on the site. While this applies only to the first virtual cluster instantiation, it can add a considerable time  latency  depending on the cluster image size and the network speed from the site to the remote repository.

In the future when the cloud scheduler is deployed to more sites, we can gather statistics on its usability and user experiences with virtual
clusters startup latencies in addition to its applicability to different scenarios.   We will also work on integrating IPOP and PRAGMA-ENT into the
cloud scheduler.  Next, we will rework the PCC software and integrate HTCondor so it is used in personal mode allowing us to keep a light footprint on
each of the PRAGMA sites.  Finally, we will investigate using the remote repository option in pragma\_boot to manage application-specific  virtual cluster
images and staging them to the sites.     We will package and document the resulting software so that new users can quickly start using the PRAGMA cloud testbed as an experimental service to test new science and infrastructure tools.
